Demystifying the Computer Science \\ PhD Admission in the US\\{\large A Handbook for International \emph{and Domestic} Students

### 2024-07-29 demystify.tex
updates

Many students lament that they get no interviews or are rejected (with strong profiles) and that the admission process seems random.  However, while it is true that the process is not perfect, it is not random.
There are many possible reasons for rejections!  Other than not having a strong profile (e.g., research potential, GPA, LoRs, SOP, poor interviews), here are some other reasons.

@@

We only review those that are assigned to us, which are already too many. Adcom chair will assign applications to reviewers based on their expertise (e.g., if a student says they want to do SE or interested in working with me).

For example, I only review those that are assigned to me.
I do not look at any other applicants, unless I know them (e.g., they contacted me) or have some special circumstances (e.g., they are a student from Vietnam). However, even if I look at them, I usually do not get involved in their evaluation.

>>>>

Many students lament that they get no interviews or are rejected (with strong profiles) and that the admission process seems random.  However, while it is true that the process is not perfect, it is not random.
Other than not having a strong profile (e.g., research potential, GPA, LoRs, SOP, poor interviews), here are some other reasons for rejections.

@@

While adcom members (in fact, any faculty) can view any application, we only review those that are assigned to us, which are already too many. Adcom chair will assign applications to reviewers based on their expertise (e.g., if a student says they want to do SE or interested in working with me), and reviewers will only review those applications. Occasionally we might look at other applications, e.g., if we know the student or have some special circumstances (e.g., if that student contacted me, I know that student, they are from Vietnam, etc). However, even if we look at them, we usually do not get involved in their evaluation.
